Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-30 overall.tex
Pass on NGE experiments and scattered space savings
Address comments on figure 5

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/titan_backfill_avail.pdf}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime in minutes vs number of
    work nodes during the experiment window time. Availability was measured
    62175 times: mean number of work nodes available 680; mean walltime
    available 680 minutes.}
\label{fig:backfill-distrib}
\end{figure}

@@

% -----------------------------------------------------------------------------
\subsection{Efficiency and Scalability of Detector Simulation on Titan}
\label{ssec:panda_titan}

@@

Initially, all the shared libraries of AthenaMP and the python scripts for the
configuration stage were stored on the Spider 2 Lustre file system. However, the
I/O patterns of the initialization and configuration stages degraded the
performance of the filesystem (Figure~\ref{}\mtnote{We may want to aggregate
some of the diagrams about lustre's experiments here}). Since Spider 2 is a
center-wide file system, this resulted in  performance degradation for all OLCF
resources and users. \mtnote{I am afraid the details about the trace are too
specific given the space constraints of a SC submission. Please feel free to
uncomment it if you disagree.}

>>>>

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/titan_backfill_avail.png}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime in minutes vs number of
    work nodes during the experiment window time. Availability was measured
    62175 times: mean number of work nodes available 680; mean walltime
    available 680 minutes.}
\label{fig:backfill-distrib}
\end{figure}

@@

% -----------------------------------------------------------------------------
\subsection{Efficiency, Scalability, and Reliability of Detector Simulation on Titan}
\label{ssec:panda_titan}

@@

\mtnote{TODO: specify that this is work in progress (see Sergey's comment) and
see how to move it to the data performance subsection}Initially, all the shared
libraries of AthenaMP and the python scripts for the configuration stage were
stored on the Spider 2 Lustre file system. However, the I/O patterns of the
initialization and configuration stages degraded the performance of the
filesystem (Figure~\ref{}\mtnote{We may want to aggregate some of the diagrams
about lustre's experiments here}). Since Spider 2 is a center-wide file system,
this resulted in  performance degradation for all OLCF resources and users.
\mtnote{I am afraid the details about the trace are too specific given the space
constraints of a SC submission. Please feel free to uncomment it if you
disagree.}
